---
output: 
  github_document:
    html_preview: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

**gglmannotate** annotates a ggplot2 with a description of a linear model.

# Installation

Install the development version from GitHub:

`devtools::install_github("wilkox/gglmannotate")`

# How to use

To add a description of a linear model to a scatter plot built with ggplot2,
just add `geom_lmannotate()`.

```{r}
library(ggplot2)
library(gglmannotate)

ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_lmannotate()
```

Grouping, for example by adding a colour aesthetic, is automatically handled.

```{r}
ggplot(mpg, aes(x = displ, y = hwy, colour = class)) +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_lmannotate()
```

Faceting is also supported.

```{r}
ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_lmannotate() +
  facet_wrap(~ class)
```

# Customising the annotation text

The annotation can be changed from the default by setting the `glue_exp`
argument to `geom_lmannotate()`, which will be parsed with the `glue()`
function from the [glue](https://glue.tidyverse.org) package. This allows
interpolation of R variables and expressions. The linear model object (the
output of `lm()`) is available inside the glue expression as the variable
`model`. For example:

```{r}
ggplot(mpg, aes(x = displ, y = hwy, colour = class)) +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_lmannotate(glue_exp = "Max residual: {signif(max(model$residuals), 2)}")
```

# Customising the annotation placement

To change the region of the plot area in which annotations will be drawn, use
the `region` argument to `geom_lmannotate()`. It takes a named numeric vector
with elements 'xmin', 'xmax', 'ymin' and 'ymax', all scaled between 0 and 1, to
define the region.

The vertical and horizontal aliment of the text within the region can be set
with `place`. It accepts the following values: "right", "bottomright", "bottom",
"bottomleft", "left", "topleft", "top", and "centre|center|middle".

```{r}
ggplot(mpg, aes(x = hwy, y = cty, colour = class)) +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_lmannotate(
    region = c(xmin = 0, xmax = 0.75, ymin = 0.75, ymax = 1),
    place = "topleft"
  )
```

The annotation text layout can be further tweaked with the `min.size`, `grow`
and `reflow` options. See the [ggfittext
package](https://github.com/wilkox/ggfittext) for full details on these
options.
