---
output: 
  github_document:
    html_preview: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

**gglmannotate** annotates a ggplot2 with a description of a linear model.

# Installation

Install the development version from GitHub:

`devtools::install_github("wilkox/gglmannotate")`

# How to use

To add a description of a linear model to a scatter plot built with ggplot2,
just add `geom_lmannotate()`.

```{r}
library(ggplot2)
library(gglmannotate)

ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_lmannotate()
```

Grouping, for example by adding a colour aesthetic, is automatically handled.

```{r}
ggplot(mpg, aes(x = displ, y = hwy, colour = class)) +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_lmannotate()
```

If you want to facet the plot, the description can be fixed in the upper right
corner with `facet_mode = TRUE`. Multiple groups in each facet are not
supported well.

```{r}
ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_lmannotate(facet_mode = TRUE) +
  facet_wrap(~ class)
```

